Decentralized Data Marketplace to Enable Trusted Machine Economy $^{\dagger}$

### 2019-12-12 paper.tex
Add extended version statement

%=================================================================
% Full title of the paper (Capitalized)
\Title{Decentralized Data Marketplace to Enable Trusted Machine Economy}

@@

%\conference{} % An extended version of a conference paper

>>>>

%=================================================================
% Full title of the paper (Capitalized)
\Title{Decentralized Data Marketplace to Enable Trusted Machine Economy $^{\dagger}$}

@@

\conference{2019 IEEE Eurasia Conference on IOT, Communication and Engineering (IEEE ECICE 2019), National Formosa University, Yunlin, Taiwan, 3–6 October, 2019} % An extended version of a conference paper
